---
title: "child2"
format: docx
editor: visual
---

# *Summary & assumptions*

For the planned study, a total of **250** patients with a possible infection must be observed given the below assumptions.

For the proposed randomized clinical study, the sample size considerations are given with the following suppositions:

 - 2 arms (arm A, B)
 - binary outcome variable (ie. rates between groups)
 - aim: to show statistical significant difference between the two arms
 - arm A is hypothecized to be 30%
 - arm B is hypothecized to be 15%
 - Power of 80%
 - Type I error rate of 5% (2-sided, equal to 2.5% one-sided)
 - 1 interim analysis (at 50% of cases, but this is flexible), 1 final analysis
 - Hwang, Shi & DeCani alpha spending function, gamma = -2
 - 1:1 randomization

```{r working_environment, include=TRUE}
# Load the package `ggplot2`
library(ggplot2)
# Load the package `rpact`
library(rpact)
```


## R outputs

```{r create_design, include=TRUE, results='hide'}
design <- getDesignGroupSequential(typeOfDesign = "asHSD", informationRates = c(0.5, 1),
  gammaA = -2)
print(design)
getDesignCharacteristics(design)
designPlan <- getSampleSizeRates(design, pi1 = 0.3, pi2 = 0.15)
summary(designPlan)
print(designPlan)
```

```{r design_output, include=TRUE, echo=FALSE, results='asis'}
print(design, markdown = TRUE)
print(getDesignCharacteristics(design), markdown = TRUE)
print(summary(designPlan), markdown = TRUE)
print(designPlan, markdown = TRUE)
```

